### 2019-11-29 data/QSFit/GC_20191128/GC.tex
major, major update

\begin{table*}
  \small
  \begin{centering}
    \begin{tabular}{l | l | c c | c c c | c}
      \hline
      \hline
        Object         &  MJD         &  \multicolumn{2}{c}{Cont. @ 1450\AA }                        &   \multicolumn{3}{c}{CIV 1549\AA}                                   & Virial product \\
                       &              &       $\nu L_{\nu}$    &         Slope                       &   Luminosity             &     FWHM           &    V$_{\rm off}$    & log($\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$)\\
                       &              & $10^{42}$ erg s$^{-1}$ & (F$_\lambda \propto \lambda^\alpha$)  & $10^{42}$ erg s$^{-1}$ &     km s$^{-1}$    &    km s$^{-1}$      &  $\log(M)$ \\
      \hline                        
                       &  53498       &  38129   $\pm$ 39      &  -1.57 $\pm$ 0.01                   &  898    $\pm$ 15         &   6024 $\pm$  120  &     944 $\pm$  33   &   9.85 $\pm$ 0.02\\
          J1205+3422   &  58538       &   8550   $\pm$ 11      &  -1.41 $\pm$ 0.01                   &  385.2  $\pm$  3.9       &   7109 $\pm$   91  &    1085 $\pm$  29   &   9.67 $\pm$ 0.01\\  
                       &  58693$^*$   &   2725   $\pm$ 40      &  -1.27 $\pm$ 0.05                   &  161    $\pm$ 22         &  14997 $\pm$ 2500  &     922 $\pm$ 690   &  10.07 $\pm$ 0.13\\  
                                      &                        &                                     &                          &                    &                     &                  \\
                       &  54553       &   3579   $\pm$ 49      &  -1.16 $\pm$ 0.07                   &  293.6  $\pm$  8.8       &   4630 $\pm$  180  &     183 $\pm$  57   &   9.11 $\pm$ 0.04\\  
          J1638+2827   &  55832       &   2340   $\pm$ 15      &  -2.17 $\pm$ 0.05                   &   84.6  $\pm$  4.2       &   4733 $\pm$  290  &     172 $\pm$  89   &   9.04 $\pm$ 0.05\\  
                       &  58583       &   7793   $\pm$ 19      &  -2.02 $\pm$ 0.01                   &  367.5  $\pm$  4.3       &   4511 $\pm$   71  &      94 $\pm$  24   &   9.25 $\pm$ 0.01\\  
                                      &                        &                                     &                          &                    &                     &                  \\
                       &  56189$^*$   &    607   $\pm$ 49      &  -0.00 $\pm$ 0.16                   &   72.8  $\pm$ 11.3       &  14993 $\pm$ 2400  &     828 $\pm$ 691   &   9.74 $\pm$ 0.14\\  
          J2228+2201   &  56960       &   7842   $\pm$ 25      &  -1.72 $\pm$ 0.02                   &  301.0  $\pm$  7.2       &   7136 $\pm$  210  &    -276 $\pm$  64   &   9.65 $\pm$ 0.03\\ 
                       &  58693       &   2388.4 $\pm$  6.8    &  -1.22 $\pm$ 0.01                   &  145.4  $\pm$  1.5       &   6084 $\pm$   83  &     168 $\pm$  28   &   9.26 $\pm$ 0.01\\  
      \hline
      \hline
    \end{tabular}
    \caption{Continuum (at 1450\AA) and CIV spectral measurements for the three QSO considered in this work, at all observation epochs, as calculated by QSFit.  The last column shows the virial product calculated as $\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$.  $^*$: The CIV line is very faint (with respect to the continuum), and the associated estimates are likely biased.}
    \label{tab:QSFit-results}
  \end{centering}
\end{table*}

>>>>

\begin{table*}
  \scriptsize
  \begin{centering}
    \begin{tabular}{l | l | c c | c c c c | c}
      \hline
      \hline
        Object         &  MJD         &  \multicolumn{2}{c}{Cont. @ 1450\AA }                        &   \multicolumn{4}{c}{CIV 1549\AA}                                                          &  Virial product \\
                       &              &       $\nu L_{\nu}$    &         Slope                       &   Luminosity             &     FWHM           &    V$_{\rm off}$    &          EW          &  log($\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$)\\
                       &              & $10^{42}$ erg s$^{-1}$ & (F$_\lambda \propto \lambda^\alpha$)  & $10^{42}$ erg s$^{-1}$ &     km s$^{-1}$    &    km s$^{-1}$      &          \AA         &  $\log(M)$ \\
      \hline                        
                       &  53498       &  38129   $\pm$ 39      &  -1.57 $\pm$ 0.01                   &  898    $\pm$ 15         &   6024 $\pm$  120  &     944 $\pm$  33   &   37.78 $\pm$  0.62  &   9.85 $\pm$ 0.02\\
          J1205+3422   &  58538       &   8550   $\pm$ 11      &  -1.41 $\pm$ 0.01                   &  385.2  $\pm$  3.9       &   7109 $\pm$   91  &    1085 $\pm$  29   &   71.32 $\pm$  0.71  &   9.67 $\pm$ 0.01\\  
                       &  58693$^*$   &   2725   $\pm$ 40      &  -1.27 $\pm$ 0.05                   &  161    $\pm$ 22         &  14997 $\pm$ 2500  &     922 $\pm$ 690   &   91.68 $\pm$ 12.73  &  10.07 $\pm$ 0.13\\  
                                      &                        &                                     &                          &                    &                     &                      &                  \\
                       &  54553       &   3579   $\pm$ 49      &  -1.16 $\pm$ 0.07                   &  293.6  $\pm$  8.8       &   4630 $\pm$  180  &     183 $\pm$  57   &  127.67 $\pm$  3.80  &   9.11 $\pm$ 0.04\\  
          J1638+2827   &  55832       &   2340   $\pm$ 15      &  -2.17 $\pm$ 0.05                   &   84.6  $\pm$  4.2       &   4733 $\pm$  290  &     172 $\pm$  89   &   59.61 $\pm$  2.98  &   9.04 $\pm$ 0.05\\  
                       &  58583       &   7793   $\pm$ 19      &  -2.02 $\pm$ 0.01                   &  367.5  $\pm$  4.3       &   4511 $\pm$   71  &      94 $\pm$  24   &   77.89 $\pm$  0.91  &   9.25 $\pm$ 0.01\\  
                                      &                        &                                     &                          &                    &                     &                      &                  \\
                       &  56189$^*$   &    607   $\pm$ 49      &  -0.00 $\pm$ 0.16                   &   72.8  $\pm$ 11.3       &  14993 $\pm$ 2400  &     828 $\pm$ 691   &  162.89 $\pm$ 25.37  &   9.74 $\pm$ 0.14\\  
          J2228+2201   &  56960       &   7842   $\pm$ 25      &  -1.72 $\pm$ 0.02                   &  301.0  $\pm$  7.2       &   7136 $\pm$  210  &    -276 $\pm$  64   &   61.99 $\pm$  1.48  &   9.65 $\pm$ 0.03\\ 
                       &  58693       &   2388.4 $\pm$  6.8    &  -1.22 $\pm$ 0.01                   &  145.4  $\pm$  1.5       &   6084 $\pm$   83  &     168 $\pm$  28   &   94.77 $\pm$  0.99  &   9.26 $\pm$ 0.01\\  
      \hline
      \hline
    \end{tabular}
    \caption{Continuum (at 1450\AA) and CIV spectral measurements for the three QSO considered in this work, at all observation epochs, as calculated by QSFit.  The last column shows the virial product calculated as $\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$.  $^*$: The CIV line is very faint (with respect to the continuum), and the associated estimates are likely biased.}
    \label{tab:QSFit-results}
  \end{centering}
\end{table*}
